landlord

### 2022-10-22 src/landlord.Rmd
imported landlord data and cleaning it.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)

MSA_landlord_data <- read_sheet("https://docs.google.com/spreadsheets/d/1zCePYRyJ5lb1Z5jvCujg17EtwqpxJN1E1_HwJL66uLM/edit#gid=122953884") 
```

```{r}
MSA_landlord_data_binary <- MSA_landlord_data %>% 
  select(cbsa, MSA, rent_control, eviction_notice_days, security_depopsit_limit_YN, notice_for_entry_days_YN)
```
